SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-05-05 papers/B1555_EdgeOn/B1555_letter.tex
change in modelling procedure description

\textbf{For each model, we explore the parameter space in the following way: 
(1) Preparation of priors: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component. We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position. The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
(2) Markov Chain Monte Carlo: In {\tt glafic}, we run MCMC to find the a proper set of parameters for further optimization. The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}

>>>>

\textbf{For each model, we explore the parameter space in the following way: 
(1) Preparation of model starting point: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component. We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position. The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
(2) First optimization: Bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec, and run optimization with amoeba algorithm in {\tt glafic} to reach a first optimal model.
(3) Markov Chain Monte Carlo: Use the parameters from optimal result as the starting point. We then run MCMC in {\tt glafic} to obtain the best-fit parameters.} 
%The smallest $\chi^2$ doesn't necessarily give a physical model. Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}
